### 2020-04-13 serial.tex
intro

The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee).
On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic.
% Despite having similar definitions, generation and serial intervals are different because serial intervals rely on the generation intervals as well as the incubation periods of an infector and an infectee.
Previous studies have often alluded to differences in their variances, despite having identical expected values, and noted that using serial-interval distribution can give different estimates of $\mathcal R$.
Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
Researchers continue to rely on both generation and serial intervals to estimate $\mathcal R$ for COVID-19 without making a clear distinction, and some even mislabel them.

The lack of clear understanding of their differences can be largely attributed to an apparent paradox.
When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number $\mathcal R$.
Likewise, since infection typically leads to symptoms, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate.
Current theory seems to contradict our biological intution.

>>>>

The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee).
On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic.
% Despite having similar definitions, generation and serial intervals are different because serial intervals rely on the generation intervals as well as the incubation periods of an infector and an infectee.
Previous studies have often alluded to differences in their variances, despite having seemingly identical expected values, and noted that using serial-interval distribution can give different estimates of $\mathcal R$.
Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
Researchers continue to rely on both generation and serial intervals to estimate $\mathcal R$ for COVID-19 without making a clear distinction, and some even mislabel them.

The lack of clear understanding of their differences can be largely attributed to an apparent paradox.
When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number $\mathcal R$.
Likewise, since infection typically leads to symptoms, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate.
Current theory suggests that using generation- and serial-interval distributions give different estimates of $\mathcal R$ and contradicts our biological intution.
